---
class: inverse, center, middle

# What are Search Engines? How do they Work?

---
# What are Search Engines?


```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "http://acronymsandslang.com/acronym_image/2574/c2e6371f31de1b922305b7f1dea6badd.jpg"
knitr::include_graphics(url)
```

Source: [Acronyms & Slang](http://acronymsandslang.com)


---
# What are Search Engines?


```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "https://www.reliablesoft.net/wp-content/uploads/2016/12/top-search-engines-oct-2020.png"
knitr::include_graphics(url)
```

Source: [ReliableSoft](https://www.reliablesoft.net/)

---
# How Do They Work? 

```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "https://mangools.com/blog/wp-content/uploads/2020/10/how-search-engines-work.png"
knitr::include_graphics(url)
```

Source: [Mangools](https://mangools.com)

---
class: font150
# Crawling 

**Crawling** is the discovery process in which search engines send out a team of robots (known as crawlers or spiders) to find new and updated content

* Fetches a few webpages, follows the links

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/crawling.png"
knitr::include_graphics(url)
```

Source: [Moz](https://moz.com/)


---
class: font140
# Indexing 

**Indexing**: search engines collect, analyze and store everything found via crawlers into data structures 

* Imagine a library of books, but containing webpages instead of books!

```{r, echo = FALSE, fig.align = "center", out.width="50%"}
url <- "https://storage.googleapis.com/algodailyrandomassets/curriculum/systems-design/search-engines/indexing.png"
knitr::include_graphics(url)
```

Source: [Algo Daily](https://algodaily.com/lessons/how-do-search-engines-work/indexing)


---
class: font150
# Ranking 

**Ranking** happens via *search engine algorithms* 

```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "https://storage.googleapis.com/algodailyrandomassets/curriculum/systems-design/search-engines/ranking.png
"
knitr::include_graphics(url)
```

Source: [Algo Daily](https://algodaily.com/lessons/how-do-search-engines-work/indexing)


---
class: font150
# Search Engine Algorithms

**Search Engine Algorithm**: evaluates intended pages and determines which should appear 

What's in the algorithm? Things such as:

1.  **Meaning of the query** 
  * What the user means, what is the search intent?
2. **Page relevance** 
  * Does page answer search query
3. **Content quality** 
  * Is page an excellent soruce of information
4. **Page usability**
  * Technical quality of page

---
class: font150
# Browsers vs Search Engines!

Important Distiction!

**Web browser**: a user friendly interface to display a webpage

VERSUS

**Search Engine**: An online tool available on a website that is accessed via a web browser

```{r, echo = FALSE, fig.align = "center", out.width="50%"}
url <- "https://www.searchenginemagazine.com/wp-content/uploads/2021/03/web-browser-vs-search-engine.jpg"
knitr::include_graphics(url)
```

Source: [Search Engine Magazine](https://www.searchenginemagazine.com/web-browser-vs-search-engine/)

---
class: inverse, center, middle

# Search Engine Marketing vs Search Engine Optimization

---
# Search Engine Marketing


```{r, echo = FALSE, fig.align = "center", out.width="90%"}
url <- "figs/sem_defined.png"
knitr::include_graphics(url)
```

---
# Search Engine Optimization 

```{r, echo = FALSE, fig.align = "center", out.width="90%"}
url <- "figs/seo_defined.png"
knitr::include_graphics(url)
```